Introducing statistics with \\texttt{intRo}

### 2014-12-11 student-paper-competition-2014/paper.Rmd
Talk about ggvis in further work

In addition to the current functionality, there are some practical improvements in the works that will make \texttt{intRo} more useful to both students and instructors. In particular, we have begun development on an \texttt{R} package which will allow \texttt{intRo} modules to be created automatically from user written \texttt{R} code. This package will generate the necessary file structure to allow the module's incorporation into \texttt{intRo} as well as translate user code to \texttt{intRo} compatible code as populates the necessary files. This will vastly improve \texttt{intRo}'s flexibility and allow it to be used in a wider range of curricula, including more advanced statistics courses.

>>>>

In addition to the current functionality, there are some practical improvements in the works that will make \texttt{intRo} more useful to both students and instructors. In particular, we have begun development on an \texttt{R} package which will allow \texttt{intRo} modules to be created automatically from user written \texttt{R} code. This package will generate the necessary file structure to allow the module's incorporation into \texttt{intRo} as well as translate user code to \texttt{intRo} compatible code as populates the necessary files. This will vastly improve \texttt{intRo}'s flexibility and allow it to be used in a wider range of curricula, including more advanced statistics courses. Furthermore, we would like to utilize the expanded interactive capabilities of \texttt{ggvis} in order to make \texttt{intRo's} plots more engaging to students. One way to do this would be implementing linked plots, in which interactions with one plot are reflected in other plots that illustrate the same data. This would be particularly useful in the regression module so that students could explore observations with high influence and leverage.
